Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-06-14 parallel-tractability-J-v9/appendix.tex
replace 'e(v1, v2)' with '(v1, v2)'

\emph{Inductive case}.
According to the induction hypothesis, the partial graph constructed after
the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
We have to show that the partial graph constructed after the $(i+1)^{th}$ iteration is
also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{\text{opt}}$ by performing Step $(\textbf{\romannumeral3})$
of Algorithm~$\mathsf{OPT}$.
Suppose that \texttt{rch}$(B_k,H)\in S_{\textit{\!\tiny rch}}$ is checked.
It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
Algorithm~$\mathsf{OPT}$ next checks that there exists a node $B'$ such that
\texttt{rch}$(B',B_k)\in S^*_{\!\tiny rch}$
and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$
according to three cases.
(1) If $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are created.
(2) If neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are also created.
In the above two cases, $H$ is a new node. Thus,
$\mathcal{G}^{i+1}$ is acyclic.
(3) If $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are also created.
For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
the algorithm does nothing.
Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.

>>>>

\emph{Inductive case}.
According to the induction hypothesis, the partial graph constructed after
the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
We have to show that the partial graph constructed after the $(i+1)^{th}$ iteration is
also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{\text{opt}}$ by performing Step $(\textbf{\romannumeral3})$
of Algorithm~$\mathsf{OPT}$.
Suppose that \texttt{rch}$(B_k,H)\in S_{\textit{\!\tiny rch}}$ is checked.
It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
Algorithm~$\mathsf{OPT}$ next checks that there exists a node $B'$ such that
\texttt{rch}$(B',B_k)\in S^*_{\!\tiny rch}$
and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$
according to three cases.
(1) If $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $(B_1, H),\ldots ,(B_n, H)$ are created.
(2) If neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $(B_1, H),\ldots ,(B_n, H)$ are also created.
In the above two cases, $H$ is a new node. Thus,
$\mathcal{G}^{i+1}$ is acyclic.
(3) If $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $(B_1, H),\ldots ,(B_n, H)$ are also created.
For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
the algorithm does nothing.
Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.

### 2018-06-14 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
replace 'e(v1, v2)' with '(v1, v2)'

\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
being constructed from $P$. The following steps are performed:
\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
\item Compute the \texttt{rch} relation $S_{\!\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
\item Compute the transitive closure $S^*_{\!\textit{\tiny rch}}$ of $S_{\!\textit{\tiny rch}}$.\label{transClos}
\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\!\textit{\tiny rch}}$
that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\!\textit{\tiny rch}}$ and $B'$ is
    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
    $e(B_1, H), \ldots, e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
    \texttt{rch}$(B_j,H)\in S_{\!\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
\end{enumerate}

>>>>

\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
being constructed from $P$. The following steps are performed:
\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
\item Compute the \texttt{rch} relation $S_{\!\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
\item Compute the transitive closure $S^*_{\!\textit{\tiny rch}}$ of $S_{\!\textit{\tiny rch}}$.\label{transClos}
\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\!\textit{\tiny rch}}$
that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\!\textit{\tiny rch}}$ and $B'$ is
    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
    $(B_1, H), \ldots, (B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
    \texttt{rch}$(B_j,H)\in S_{\!\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
\end{enumerate}
